---
title: "Project EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in Data

```{r}
library(fpp)
lty <- read.csv('10LTY.csv')
cpi <- read.csv('CPI.csv')
mmm <- read.csv('MMMFFAQ027S.csv')
tb <- read.csv('TB3MS.csv')


# MMM 1974-01-01 to 2021-10-1
mmm <- tail(mmm, -113)
lty <- lty[169:742,]
cpi <- cpi[325:898,]
tb <- tb[481:1054,]
lty_tb_diff <- lty$IRLTLT01USM156N - tb$TB3MS
lty_tb <- data.frame(DATE = cpi$DATE, value = lty_tb_diff)
```

## Cubic Spline interpolation for MMM

```{r}
# Check date with other time series first

cpi$DATE <- as.Date(cpi$DATE)
mmm$DATE <- as.Date(mmm$DATE)
months <- lapply(X = mmm$DATE, FUN = seq.Date, by = "month", length.out = 3)
months <- data.frame(DATE = do.call(what = c, months))


library(dplyr)
monthly_data <- left_join(x = months, y = mmm, by = "DATE")
monthly_data <- monthly_data[-c(575,576),]
library(zoo)
monthly_data$MMMFFAQ027S <- na.spline(object = monthly_data$MMMFFAQ027S)
```

## EDA for MMM

```{r}
tsdisplay(monthly_data$MMMFFAQ027S, main = 'Money Market Fund from Spline Interpolation')
```

As expected, since the data is generated through spline interpolation, there will bound to be autocorrelation present and the series is not stationary.

## EDA for CPI

```{r}
cpi_ts <- ts(cpi$CPIAUCSL, start = c(1974,1), frequency = 12)
tsdisplay(cpi_ts, main = 'Consumer Price Index (all urban consumers)')
```
### Stationary test

```{r}
adf.test(cpi_ts)
kpss.test(cpi_ts, null = 'Trend')
kpss.test(cpi_ts)
```

We see that the CPI data is non-stationary.

## EDA for Difference between LTY and TB

### Plots
```{r}
lty_tb_ts <- ts(lty_tb_diff, start = c(1974,1), frequency = 12)


tsdisplay(lty_tb_ts, main = 'Difference between Long Term Yeild and Treasury Bill Rate')
```
### Stationary Test

```{r}
adf.test(lty_tb_ts)
kpss.test(lty_tb_ts, null = 'Trend')
kpss.test(lty_tb_ts)
```
We see that the difference between long term yield and treasury bill is stationary.

## Write out csv files

```{r}
write.csv(monthly_data,'C:/Users/bruce/Desktop/Spring 2022/Time Series/Project/data/MMM.csv', row.names = FALSE)
write.csv(cpi,'C:/Users/bruce/Desktop/Spring 2022/Time Series/Project/data/cpi.csv', row.names = FALSE)
write.csv(lty_tb,'C:/Users/bruce/Desktop/Spring 2022/Time Series/Project/data/LTY_TB_Diff.csv', row.names = FALSE)


```

