---
title: "bond"
output: html_document
---


## Part 1: EDA
```{r setup, include=FALSE}
library(tseries)
```


```{r cars}
bond= read.csv('bond.csv')
bond = bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2021-10-01", ]
bond
```

```{r}
library(anytime)
bond$observation_date= anydate(bond$observation_date)
```

```{r}
class(bond$observation_date)
```


```{r}
baa = bond[,2]
aaa = bond[,4]
spread = bond$BAA10YM
plot(baa ~ bond$observation_date, type = "l", main = "Baa Monthly Corporate Bond Yield")
```
```{r}
plot(aaa~ bond$observation_date, type = "l", main = "AAA Monthly Corporate Bond Yield")
```

## kpss test

```{r}
kpss.test(baa, null = "Trend")
kpss.test(aaa, null = "Trend")
kpss.test(spread, null = "Trend")
```

### non stationary even after removing trends

```{r}
plot(spread~ bond$observation_date, type = "l", main = "Credit Spread")
```
```{r}
baa_aaa = lm(baa~ aaa, data=bond)
summary(baa_aaa)
```

```{r}
baa_credit = lm(baa~ spread, data=bond)
summary(baa_credit)
```

```{r}
acf(baa)
pacf(baa)
```

```{r}
acf(spread)
pacf(spread)
```
```{r}
plot(baa_aaa$residuals)
```
```{r}
plot(baa_credit$residuals)
```
```{r}
bond$aaa_spread = bond$BAA - bond$AAA
aaa_spread = bond$aaa_spread
```

```{r}
plot(bond$aaa_spread~ bond$observation_date, type = "l", main = "Spread Against AAA Monthly Corporate Bond Yield")
```
```{r}
acf(aaa_spread)
```
```{r}
pacf(aaa_spread)
```
```{r}
aaa_spread_lm = lm(baa~aaa_spread)
summary(aaa_spread_lm)
```

```{r}
plot(aaa_spread_lm$residuals)
```
```{r}
library(forecast)
arima_baa = auto.arima(baa)
```

```{r}
acf(arima_baa$residuals)
pacf(arima_baa$residuals)
```

```{r}
plot(arima_baa$residuals)
```
```{r}
arima_spread = auto.arima(spread)
arima_spread
```

```{r}
acf(arima_spread$residuals)
pacf(arima_spread$residuals)
plot(arima_spread$residuals)
```

### heteroskedasticity tests

```{r}
library(lmtest)
```


```{r}
Box.test(arima_baa$residuals, type= "Ljung")
Box.test(arima_spread$residuals, type= "Ljung")
```

# Part 2: Fitting Model

### train test split

```{r}
train = bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2020-10-01",][,1:2]
test = bond[bond$observation_date >= "2020-11-01" & bond$observation_date <= "2021-10-01",][,1:2]
```

```{r}
train_aaa_temp = bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2020-10-01",]
train_aaa = train_aaa_temp$AAA
test_aaa_temp = bond[bond$observation_date >= "2020-11-01" & bond$observation_date <= "2021-10-01",]
test_aaa = test_aaa_temp$AAA
```

```{r}
train_baa_temp = bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2020-10-01",]
train_baa = train_baa_temp$BAA
test_baa_temp = bond[bond$observation_date >= "2020-11-01" & bond$observation_date <= "2021-10-01",]
test_baa = test_baa_temp$BAA
```

```{r}
baa_train1 <- bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2016-10-01",]$BAA
baa_val1 <- bond[bond$observation_date >= "2016-11-01" & bond$observation_date <= "2017-10-01",]$BAA 
baa_train2 <- bond[bond$observation_date >= "1975-01-01" & bond$observation_date <= "2017-10-01",]$BAA 
baa_val2 <- bond[bond$observation_date >= "2017-11-01" & bond$observation_date <= "2018-10-01",]$BAA  
baa_train3 <- bond[bond$observation_date >= "1976-11-01" & bond$observation_date <= "2018-10-01",]$BAA 
baa_val3 <- bond[bond$observation_date >= "2018-11-01" & bond$observation_date <= "2019-10-01",]$BAA 

```

```{r}
aaa_train1 <- bond[bond$observation_date >= "1974-01-01" & bond$observation_date <= "2016-10-01",]$AAA
aaa_val1 <- bond[bond$observation_date >= "2016-11-01" & bond$observation_date <= "2017-10-01",]$AAA 
aaa_train2 <- bond[bond$observation_date >= "1975-01-01" & bond$observation_date <= "2017-10-01",]$AAA 
aaa_val2 <- bond[bond$observation_date >= "2017-11-01" & bond$observation_date <= "2018-10-01",]$AAA  
aaa_train3 <- bond[bond$observation_date >= "1976-11-01" & bond$observation_date <= "2018-10-01",]$AAA 
aaa_val3 <- bond[bond$observation_date >= "2018-11-01" & bond$observation_date <= "2019-10-01",]$AAA 
```


## Cointegration

### Granger Causality Test
```{r}
library(lmtest)
```

```{r}
grangertest(aaa, baa, order = 2)
```

### at 0.05 significance level, we reject the null hypothesis that aaa does not granger - cause baa; it is reasonable to use aaa yield to predict baa


```{r}
grangertest(baa, aaa, order = 2)
```


```{r}
#install.packages("dynlm")
library(dynlm)
```

```{r}
coint_model = dynlm(baa~aaa)
summary(coint_model)
res_coint_model = residuals(coint_model)
```

```{r}
library(urca)
ur.df(res_coint_model)
```


reject the null hypothesis - there is cointegration relationship

## Predicting using cointegration model


```{r}
ts_baa_train = ts(baa, start = c(1974,1), end = c(2020,9), frequency = 12)
ts_baa_test = ts(baa, start = c(2020,10), end = c(2021,10), frequency = 12)
ts_aaa_train = ts(aaa, start = c(1974,1), end = c(2020,9), frequency = 12)
ts_aaa_test = ts(aaa, start = c(2020,10), end = c(2021,11), frequency = 12)
```



```{r}
data <- cbind(train_baa,train_aaa)
cajo <- ca.jo(data, ecdet = "none", type="eigen", K=2, spec="longrun")
summary(cajo)
```

## fitting a Vector Error Correction Model


```{r}
library(Metrics)
library(tsDyn)
VECM_tsDyn = VECM(cbind(train_baa, train_aaa), lag=2, r=1,estim = "ML")
VECM_predict= VECM_tsDyn$residuals[,1]+ train_baa
matplot(cbind(VECM_predict, train_baa), type="l")
legend("topright",legend=c("Forecast train","Actual train"),
       col=c("black","red"), lty=1:5
       )
smape(VECM_predict, train_baa)
```

```{r}
plot(VECM_tsDyn$residuals[,1], type="l")
hist(VECM_tsDyn$residuals[,1])
```




```{r}
library(Metrics)
predvecm<-predict(VECM_tsDyn, n.ahead=12)
smape(predvecm[,1], test_baa)
```

```{r}
Box.test(VECM_tsDyn$residuals[,1], type= "Ljung")
```

### cross validation


```{r}
VECM_val1 = VECM(cbind(baa_train1, aaa_train1), lag=2, r=1,estim = "ML")
VECM_predict_val1= VECM_val1$residuals[,1]+ baa_train1
smape(VECM_predict_val1, baa_train1)
```

```{r}
library(Metrics)
predvecm1<-predict(VECM_val1, n.ahead=12)
smape(predvecm1[,1], baa_val1)
```

```{r}
VECM_val2 = VECM(cbind(baa_train2, aaa_train2), lag=2, r=1,estim = "ML")
VECM_predict_val2= VECM_val2$residuals[,1]+ baa_train2
smape(VECM_predict_val2, baa_train2)
```
```{r}
predvecm2<-predict(VECM_val2, n.ahead=12)
smape(predvecm2[,1], baa_val2)
```
```{r}
VECM_val3 = VECM(cbind(baa_train3, aaa_train3), lag=2, r=1,estim = "ML")
VECM_predict_val3= VECM_val3$residuals[,1]+ baa_train3
smape(VECM_predict_val3, baa_train3)
```
```{r}
predvecm3<-predict(VECM_val3, n.ahead=12)
smape(predvecm3[,1], baa_val3)
```


## Prophet

```{r}
#install.packages("prophet")
library(prophet)
```

```{r}
colnames(train) <- c("ds", "y")
m = prophet(train)
```
```{r}
future <- make_future_dataframe(m, periods = 12)
forecast <- predict(m, future)
```

```{r}
plot(m, forecast)
```

### the fit doesn't look good; try multivarate by adding AAA yield instead


## multivariate

```{r}
train$AAA= train_aaa
m=prophet(yearly.seasonality = T)
m <- add_regressor(m, 'AAA')
m <- fit.prophet(m, train)
```

```{r}
future$AAA = bond[1:574,4]
forecast <- predict(m, future)
```

### multivariate prophet evaluation - only add aaa

```{r}
plot(m,forecast)
```

```{r}
prophet_plot_components(m, forecast)
```

```{r}
library(Metrics)
prophet_predicted = forecast$yhat
length(prophet_predicted)
residuals_prophet = bond$BAA - prophet_predicted
plot(residuals_prophet, type="l")
hist(residuals_prophet)
smape(bond$BAA, prophet_predicted)
smape(test_baa, tail(prophet_predicted,12))
```

```{r}
Box.test(residuals_prophet, type= "Ljung")
```



