---
title: "R Notebook"
output:
  html_document:
    df_print: paged
fig_width: 6
fig_height: 4
---


```{r}
getwd()
setwd(dir = '/Users/nihaalz/Desktop/UChicago/2021-2022/Q3_Spring2022/Time Series/Project/MSCA-Time-Series-main/data/')

library(readxl)
library(xts)
library(zoo)
library(tseries)
library(forecast)
library(Metrics)
library(car)
library(lubridate)
```

READING IN DATA
```{r}
trsm3m = read.csv('3MTBSMR.csv',sep = ' ')
bond = read.csv('bond.csv')
cpi = read.csv('cpi.csv')
dividend = read.csv('Dividend_New.csv')
ltgby = read.csv('LTGBY.csv',sep = ' ')
term_spread = read.csv('LTY_TB_Diff.csv')
# money market mutual fund
mmm = read.csv('MMM.csv')
sp_index = read.csv('S&P.csv')
sp500pe = read.csv('SP500PER.csv',sep = ' ')
monthly_returns = read.csv('Sum of Monthly Squared Return.csv') # stationary
```

DATA CLEANING
```{r}
# treasury bill
trsm3m = ts(trsm3m$X3.Month.Treasury.Bill.Secondary.Market.Rate,start=c(1974,1),frequency = 12)

# aaa and baa bonds
bond$observation_date = as.Date(bond$observation_date,'%Y-%m-%d')
bond = bond[bond$observation_date >= as.Date('1974-01-01', format='%Y-%m-%d'),]
bond = bond[bond$observation_date <= as.Date('2021-10-01', format='%Y-%m-%d'),]

baa = ts(bond$BAA,start=c(1974,1),frequency = 12)
baa10ym = ts(bond$BAA10YM,start=c(1974,1),frequency = 12)
aaa = ts(bond$AAA,start=c(1974,1),frequency = 12)

# consumer price index
cpi$DATE = as.Date(cpi$DATE,'%Y-%m-%d')
cpi = cpi[cpi$DATE <= as.Date('2021-10-01', format='%Y-%m-%d'),]
cpi = ts(cpi$CPIAUCSL,start=c(1974,1),frequency = 12)

# dividend
dividend =  dividend[nrow(dividend):1,]
dividend = ts(dividend$Value,start=c(1974,1),frequency = 12)

# government bond yields
ltgby$Date = as.Date(ltgby$Date,'%Y-%m-%d')
ltgby = ts(ltgby$Long.Term.Government.Bond.Yields,start=c(1974,1),frequency = 12)

# term spread
term_spread$DATE = as.Date(term_spread$DATE,'%Y-%m-%d')
term_spread = ts(term_spread$value,start=c(1974,1),frequency = 12)

# money market mutual fund
mmm$DATE = as.Date(mmm$DATE,format='%Y-%m-%d')
mmm = ts(mmm$MMMFFAQ027S,start=c(1974,1),frequency = 12)

# sp index
sp_index$Day = substr(sp_index$Date,9,10)
sp_index = sp_index[sp_index$Day == '01',]
sp_index$Date = as.Date(sp_index$Date,'%Y-%m-%d')
#sp_index = sp_index[sp_index$Date >= as.Date('1974-01-01', format='%Y-%m-%d'),]
#sp_index = sp_index[sp_index$Date <= as.Date('2021-10-01', format='%Y-%m-%d'),]
sp_index = ts(sp_index$Value,start=c(1974,1),frequency = 12)

# sp500 pe ratio
sp500pe$Day = substr(sp500pe$Date,9,10)
sp500pe = sp500pe[sp500pe$Day == '01',]
sp500pe = ts(sp500pe$S.P.500.PE.Ratio,start=c(1974,1),frequency = 12)

# sum of monthly squared return
monthly_returns = ts(monthly_returns$value,start=c(1974,1),frequency = 12)
```

EDA AND STATIONARITY TESTS
```{r}
par(mfrow=c(3,4),mar=c(1,1,1,1))
plot.ts(trsm3m)
plot.ts(baa)
plot.ts(baa10ym)
plot.ts(aaa)
plot.ts(cpi)
plot.ts(dividend)
plot.ts(ltgby)
plot.ts(term_spread)
plot.ts(mmm)
plot.ts(sp_index)
plot.ts(sp500pe)
plot.ts(monthly_returns)
```

```{r}
par(mfrow=c(3,4),mar=c(1,1,1,1))
acf(trsm3m)
acf(baa)
acf(baa10ym)
acf(aaa)
acf(cpi)
acf(dividend)
acf(ltgby)
acf(term_spread)
acf(mmm)
acf(sp_index)
acf(sp500pe)
acf(monthly_returns)
```


```{r}
kpss.test(trsm3m,null='Trend') #non stationary
kpss.test(baa,null='Trend') # non stationary
kpss.test(baa10ym,null='Trend') # non stationary
kpss.test(aaa,null='Trend') # non stationary
kpss.test(cpi,null='Trend') # non stationary
kpss.test(dividend,null='Trend') # non stationary
kpss.test(ltgby,null='Trend') # non stationary
kpss.test(term_spread,null='Trend') # non stationary
kpss.test(mmm,null='Trend') # non stationary
kpss.test(sp_index,null='Trend') # non stationary
kpss.test(sp500pe,null='Trend') # non stationary 
kpss.test(monthly_returns,null='Trend') # stationary 
```

CONVERTING NON STATIONARY TIME SERIES TO STATIONARY BY TAKING 1ST ORDER DIFFERENCE
```{r}
trsm3m_diff = diff(log(trsm3m),lag=1)
baa_diff = diff(log(baa),lag=1)
baa10ym_diff = diff(log(baa10ym),lag=1)
aaa_diff = diff(log(aaa),lag=1)
cpi_diff = diff(log(cpi),lag=1)
dividend_diff = diff(log(dividend),lag=1)
ltgby_diff = diff(log(ltgby),lag=1)
term_spread_diff = diff(term_spread,lag=1)
mmm_diff = diff(log(mmm),lag=1)
sp_index_diff = diff(log(sp_index),lag=1)
sp500pe_diff = diff(log(sp500pe),lag=1)
monthly_returns_diff = diff(log(monthly_returns),lag=1)
```

TESTING FOR STATIONARITY AFTER TAKING 1ST ORDER LAG
```{r}
kpss.test(trsm3m_diff,null='Trend') # stationary
kpss.test(baa_diff,null='Trend') #  stationary
kpss.test(baa10ym_diff,null='Trend') #  stationary
kpss.test(aaa_diff,null='Trend') #  stationary
kpss.test(cpi_diff,null='Trend') # non stationary
kpss.test(dividend_diff,null='Trend') #  stationary
kpss.test(ltgby_diff,null='Trend') #  stationary
kpss.test(term_spread_diff,null='Trend') #  stationary
kpss.test(mmm_diff,null='Trend') # non stationary
kpss.test(sp_index_diff,null='Trend') #  stationary
kpss.test(sp500pe_diff,null='Trend') #  stationary 
kpss.test(monthly_returns_diff,null='Trend') # stationary 
```

ARIMA MODEL ON BAA
```{r}
arima_model = auto.arima(baa)
summary(arima_model)
```

K FOLD CROSS VALIDATION ON ARIMA MODEL

FOLD 1: 1974-2016, validate on 2017
FOLD 2: 1974-2017, validate on 2018
FOLD 3: 1974-2018, validate on 2019

```{r}
# fold 1
baa.fold1 = window(baa,1974,c(2016,12))
baa.val1 = window(baa,2017,c(2017,12))

arima1 = auto.arima(baa.fold1)
arima1.pred = forecast(arima1,h=12)$mean
smape1 = smape(baa.val1,arima1.pred)

arima_smape = c()
arima_smape = append(arima_smape,smape1)
```

```{r}
plot(arima1$residuals)
```
```{r}
 Box.test(arima1$residuals,type='Ljung')
```


```{r}
# fold 2
baa.fold2 = window(baa,1974,c(2017,12))
baa.val2 = window(baa,2018,c(2018,12))

arima2 = auto.arima(baa.fold2)
arima2.pred = forecast(arima2,h=12)$mean
smape2 = smape(baa.val2,arima2.pred)

arima_smape = append(arima_smape,smape2)
```

```{r}
plot(arima2$residuals)
```

```{r}
 Box.test(arima2$residuals,type='Ljung')
```


```{r}
# fold 3
baa.fold3 = window(baa,1974,c(2018,12))
baa.val3 = window(baa,2019,c(2019,12))

arima3 = auto.arima(baa.fold3)
arima3.pred = forecast(arima3,h=12)$mean
smape3 = smape(baa.val3,arima3.pred)

arima_smape = append(arima_smape,smape3)
```

```{r}
plot(arima3$residuals,main='ARIMA Residuals')
```
```{r}
plot(forecast(arima3,h=12),main='ARIMA Forecast')
```

```{r}
 Box.test(arima3$residuals,type='Ljung')
```


```{r}
arima_smape
mean(arima_smape)
```

ARIMA MODEL WITH FORECASTING
```{r}
baa_train = window(baa,1974, c(2020,9))
baa_test = window(baa, c(2020,10),c(2021,10))

baa_arima = auto.arima(baa_train)
baa_arima_pred = forecast(baa_arima,h=12)$mean

baa_smape = smape(baa_test,baa_arima_pred)
baa_smape
```

```{r}
plot(baa_arima$residuals,main='ARIMA Residuals')
```

```{r}
 Box.test(baa_arima$residuals,type='Ljung')
```


```{r}
plot(forecast(baa_arima,h=12),main='ARIMA Forecast')
```

```{r}
summary(baa_arima)
```


DYNAMIC REGRESSION MODEL
```{r}
default_yield_spread = aaa_diff - baa_diff
default_return_spread = trsm3m_diff - baa_diff
  
predictors = cbind(default_yield_spread,baa10ym_diff,default_return_spread,dividend_diff,ltgby_diff,term_spread_diff,sp_index_diff,sp500pe_diff,monthly_returns_diff)
dynamic_model = auto.arima(baa_diff, xreg = predictors)
summary(dynamic_model)
```

K FOLD CROSS VALIDATION ON DYNAMIC REGRESSION

FOLD 1: 1974-2016, validate on 2017
FOLD 2: 1974-2017, validate on 2018
FOLD 3: 1974-2018, validate on 2019

```{r}
# fold 1

x_train1 = window(predictors,1974,c(2016,12))
y_train1 = window(baa_diff,1974,c(2016,12))

x_test1 = window(predictors, 2017, c(2017,12))
y_test1 = window(baa_diff, 2017, c(2017,12))

dynamic1 = auto.arima(y_train1, xreg = x_train1)
dynamic.pred1 = forecast(dynamic1,h=12,xreg = x_test1)$mean

dynamic.smape = c()
dynamic.smape1 = smape(y_test1,dynamic.pred1)
dynamic.smape = append(dynamic.smape,dynamic.smape1)

```

```{r}
plot(dynamic1$residuals)
```

```{r}
 Box.test(dynamic1$residuals,type='Ljung')
```


```{r}
# fold 2

x_train2 = window(predictors,1974,c(2017,12))
y_train2 = window(baa_diff,1974,c(2017,12))

x_test2 = window(predictors, 2018, c(2018,12))
y_test2 = window(baa_diff, 2018, c(2018,12))

dynamic2 = auto.arima(y_train2, xreg = x_train2)
dynamic.pred2 = forecast(dynamic2,h=12,xreg=x_test2)$mean

dynamic.smape2 = smape(y_test2,dynamic.pred2)
dynamic.smape = append(dynamic.smape,dynamic.smape2)

```

```{r}
plot(dynamic2$residuals)
```

```{r}
 Box.test(dynamic2$residuals,type='Ljung')
```


```{r}
# fold 3

x_train3 = window(predictors,1974,c(2018,12))
y_train3 = window(baa_diff,1974,c(2018,12))

x_test3 = window(predictors, 2019, c(2019,12))
y_test3 = window(baa_diff, 2019, c(2019,12))

dynamic3 = auto.arima(y_train3, xreg = x_train3)
dynamic.pred3 = forecast(dynamic3,h=12,xreg=x_test3)$mean

dynamic.smape3 = smape(y_test3,dynamic.pred3)
dynamic.smape = append(dynamic.smape,dynamic.smape3)


```

```{r}
plot(dynamic3$residuals,main='Dynamic Regression Residuals')
```

```{r}
 Box.test(dynamic3$residuals,type='Ljung')
```

```{r}
plot(forecast(dynamic3,h=12,xreg=x_test3),main='Dynamic Regression Forecast')
```

```{r}
dynamic.smape
mean(dynamic.smape)
```


DYNAMIC REGRESSION MODEL WITH FORECASTING
```{r}
x_train = window(predictors,1974,c(2020,9))
y_train = window(baa_diff,1974,c(2020,9))

x_test = window(predictors, c(2020,10), c(2021,10))
y_test = window(baa_diff, c(2020,10), c(2021,10))

dynamic = auto.arima(y_train, xreg = x_train)
dynamic.pred = forecast(dynamic,h=12,xreg=x_test)$mean

dynamic.smape = smape(y_test,dynamic.pred)
dynamic.smape
```

```{r}
plot(dynamic$residuals,main='Dynamic Regression Residuals')
```

```{r}
 Box.test(dynamic$residuals,type='Ljung')
```

```{r}
plot(forecast(dynamic,h=12,xreg=x_test),main='Dynamic Regression Forecast')
```

